TrueSkill Through Time: the \proglang{Python} Package

### 2020-08-06 article.tex
Paper TTT: cambios en ilustration

This tutorial will guide you through some of typical \textbf{TTT} package application.
Familiarity with Python is assumed, so if you are new to Pythom there is plenty of online documentation like the official Python documentation
page at \href{http://www.python.org/doc/}{\textcolor{blue}{http://www.python.org/doc/}}.
In addition to the module \textbf{TTT}, the libraries collections, dateutil and mathematics(Gaussian) are also required.
In this section its show some applications, starting with an example of TrueSkill of 1vs1, then an example with a data set, and the last one a first example of Trueskill Through Time.

\subsection{Example 1: TrueSkill 1vs1}
The first examples is the most basic one we figure out. Its one of the first examples in the official python package of Trueskill. 
Our library, its almost four times faster than the official, when computing posteriors.
% explicar el ejemplo de que esta pasando
% presentar variables, mapeo entre ejemplo  y teoria
% sacar linea en blanco, y sacar la linea entre el import y lo otro
\lstinputlisting{./code/Example1.py}
\begin{lstlisting}
[Out]: Posterior:  TrueSkill.Rating(mu=29.205, sigma=7.194, beta=4.167, noise=0.083) Mean:  29.2052208700336 Variance:  7.194481348831081
\end{lstlisting}
% explicar la info que sale del resutlado
% no es la varianza es el desvio
% contar la expresion de result
%explicar que es Rating, draw prob 0
% la habilidad del jugador 1 es babla
The time average of this example in a microprocessor i7 babla, its about $4.5$ $10^{-5}$, and for the python package its about $1.9$ $10^{-4}$. About four times faster.

% sacar esto del tiempo aca y hacerlo en el data set y como escala a medida que agrando el data set, presentarlo en una tabla de tiempos.
% 3 o 4 resultados
\subsection{Example 2: TrueSkill data-set}
Another example we want to show how TrueSkill can be used with a data set. 
To start, we will show the implementation for the users that already are familiar with the original TrueSkill package making an almost same implementation and then we will show the way that this package its intend to be used. 
With this way, the use of \textbf{TTT} its trivial. 
For the first and second case we will use as input the Table \ref{tab:csvExample2}. Its important to have the input "Result" as the same format as shown in the table.
In this first case we will use the library Pandas, but it can be done with out it, the only important its how to upload the data set and loop with it. For the second case we still using Pandas but only to keep the same way of reading the CSV file that the first one. 
In this case we don't need to loop manually through the data set.

@@

In this example, we use the method get, so we can use the global prior only for the first game for each player.
% sacar el sys
% explicar como usar la salida
\subsection{Example 2 new implementation}
\lstinputlisting{./code/Example2-1.py}
[Out]:Time $2.8$ $10^{-3}$ seconds
% repetir los de que es mas comodo por estar en una linea
% sacar batch number
\subsection{Example 3: Trueskill True Time}
One of the advantage of \textbf{TTT}, its the way that the algorithm pass information to the past to the future and vice versa, getting a more accurate estimation. 
In addition, it can define a temporal batch were its suppose that in there the order of the games it doesn't matter. 
For that, we use the next example. 
Three player, three games, that each one wins one game and lose the other one. 
So if we do TrueSkill, the order of how we compute the games will have importance, making at the end three player with three different skill. 
With \textbf{TTT} this kind of problem its solve.
% sacar como es TTT yaque se comento antes. poder poner como ya se menciono....
\lstinputlisting{./code/Example3.py}

% aclarar que no hay implementacion de esto, y por que es mejor.
% y aclarar que pasa si sale con TTT y que saldria si corro trueskill
% poner el el grafico que corro trueskill
%cambiar nombre de throguth time por trueskill
To extend this example to a data set with more games, the only thing that matter is to pass the information in the format show. 
In first place is the composition of games, that its a list, that contain a list for each game, that it have another list for each team. 
So its a list of list of list. 
Then its have a list of list of results, where each element is a list of numbers, representing the result of each team in each game. 
The next important input its the time batches, as default it will make each game in a

>>>>

This tutorial will guide you through some of typical \textbf{TTT} package application.
Familiarity with Python is assumed, so if you are new to Python there is plenty of online documentation like the official Python documentation
page at \href{http://www.python.org/doc/}{\textcolor{blue}{http://www.python.org/doc/}}.
In addition to the module \textbf{TTT}, the libraries collections, dateutil and mathematics(Gaussian) are also required.
In this section its show some applications, starting with an example of TrueSkill of 1vs1, then an example with a data set, and the last one a first example of Trueskill Through Time.

\subsection{Example 1: TrueSkill 1vs1}
The first examples is the most basic one we figure out. Its one of the first examples in the official python package of \texttt{Trueskill}.
In this case, we consider a game that can be won or lost but not tied, in which two players face each other and we want to update our prior of them knowing the result of it.
For that we start creating an environment of \texttt{TrueSkill}, specifying the parameter \texttt{draw\_probability} to zero, not to consider the possibility of a tie.
Then we define the prior of each player. 
Because in this case we don't know anithing of each, they start with a default prior.
This one can be set up at will.
The parameters of this, is the mean and standard deviation of the skill (mu and sigma), the standard deviation of the performance (beta), and the noise add it in the posterior, as the method suggest (noise).
The result of the game, is in format of a list, with a number for each player, meaning 0 for the one that lost the game, and 1 for the winner.
After this, define the game with the method \texttt{Game}, and calculate this the posterior of the player with the method \texttt{posterior}.
We update the prior of each player with the posterior.

Also we show how to get some of the parameters, using the method with name of the parameters in this object.

Our library, its almost four times faster than the official, when computing posteriors.
% explicar el ejemplo de que esta pasando
% presentar variables, mapeo entre ejemplo  y teoria
\lstinputlisting{./code/Example1.py}
\begin{lstlisting}
[Out]: Posterior:  TrueSkill.Rating(mu=29.205, sigma=7.194, beta=4.167, noise=0.083) Mean:  29.2052208700336 Variance:  7.194481348831081
\end{lstlisting}

As we can see, we print the posterior of one of them, showing as the object of the class \texttt{TrueSkill}, with the new parameters.
Esta mal la forma en que devuelve, player 1 deberia haber empeorado por perder. Ademas creo que sort teams solo funca para dos equipos
This show that player 2, that won the game, update his skill with mean $25$ and standard deviation $25/3$ to have a mean $29.20$ and standard deviation $7.19$ approximately.

% la habilidad del jugador 1 es babla
%The time average of this example in a microprocessor i7 babla, its about $4.5$ $10^{-5}$, and for the python package its about $1.9$ $10^{-4}$. About four times faster.
Tabla de valores temporales, esperar a tener el codigo optimizado 
% sacar esto del tiempo aca y hacerlo en el data set y como escala a medida que agrando el data set, presentarlo en una tabla de tiempos.
% 3 o 4 resultados
\subsection{Example 2: TrueSkill data-set}
Another example we want to show how TrueSkill can be used with a data set. 
To start, we will show the implementation for the users that already are familiar with the original TrueSkill package making an almost same implementation and then we will show the way that this package its intend to be used. 
With this way, the use of \textbf{TTT} its trivial. 
For the first and second case we will use as input the Table \ref{tab:csvExample2}. Its important to have the input "Result" as the same format as shown in the table.
In this first case we will use the library Pandas, but it can be done with out it, the only important its how to upload the data set and loop with it. For the second case we still using Pandas but only to keep the same way of reading the CSV file that the first one. 
In this case we don't need to loop manually through the data set.

@@

In this example, we use the method get, so we can use the global prior only for the first game for each player.
As the same way of the first example, we are updating the prior of each player with the posterior of each game.
In this case we are saving this in a dictionary with the name of each player as key.
Printing at the end this, we will have each player with the latest posterior.

% explicar como usar la salida
\subsection{Example 2 new implementation}
\lstinputlisting{./code/Example2-1.py}
[Out]:Time $2.8$ $10^{-3}$ seconds

In this new implementation, we create a object of the method \texttt{history}, passing it the game composition, that is a list with a list for each game, and inside one list for each team, and also passing the result of each game.
REVISAR SI PASE BIEN EL RESULT.
Then using the method \texttt{trueskill} in this object, we compute the posteriors. 
ONLINE NO SERIA TRUE PARA SER CMOMO TRUESKILL?
For last, we can see the last posterior of each player, calling the method \texttt{posteriors\_players()}
Like we can see, the new way of implementation its more compact and simple than the original.

\subsection{Example 3: Trueskill True Time}
As it was mentioned already, one of the advantage of \textbf{TTT}, its the way that the algorithm pass information to the past to the future and vice versa, getting a more accurate estimation.
This package is the first implementation of this method, beside the original \texttt{Microsoft} package in \texttt{F\#}, of not free access. CHEQUEAR ESTO
For that, we use the next example. 
Three player, three games, that each one wins one game and lose the other one. 
So if we do TrueSkill, the order of how we compute the games will have importance, making at the end three player with three different skill. 
With \textbf{TTT} this kind of problem its solve.

\lstinputlisting{./code/Example3.py}
\vspace{-0.3cm}
[Out]:Poner Trueskill

[Out]:Poner TTT
\vspace{0.3cm}
We print the posteriors in two instance, to the reason for comparing the posteriors with \texttt{TrueSkill} vanilla, and with \texttt{TTT}.
The 
% y aclarar que pasa si sale con TTT y que saldria si corro trueskill
% poner el el grafico que corro trueskill
%cambiar nombre de throguth time por trueskill
To extend this example to a data set with more games, the only thing that matter is to pass the information in the format show. 
In first place is the composition of games, that its a list, that contain a list for each game, that it have another list for each team. 
So its a list of list of list. 
Then its have a list of list of results, where each element is a list of numbers, representing the result of each team in each game. 
The next important input its the time batches, as default it will make each game in a
